---
title: "FunctionFactories"
author: "Jill MacKay"
date: "8 May 2019"
output: html_document
---



```{r}
library(rlang)
library(ggplot2)
library(scales)
```
https://advanced-r-solutions.rbind.io/function-factories.html

# 10.2.6 Exercises
## 1 The definition of force() is simple:

```{r}
force
```

## Why is it better to force(x) instead of just x?

If you change a binding after creating a function factory it will be lazily evaluated





## 2 Base R contains two function factories, approxfun() and ecdf(). Read their documentation and experiment to figure out what the functions do and what they return.

```{r}
approxfun


```



## 3 Create a function pick() that takes an index, i, as an argument and returns a function with an argument x that subsets x with i.

```{r}
pick(1)(x)
# should be equivalent to
x[[1]]

lapply(mtcars, pick(5))
# should be equivalent to
lapply(mtcars, function(x) x[[5]])
```




## Create a function that creates functions that compute the ith central moment of a numeric vector. You can test it by running the following code:

```{r}
m1 <- moment(1)
m2 <- moment(2)

x <- runif(100)
stopifnot(all.equal(m1(x), 0))
stopifnot(all.equal(m2(x), var(x) * 99 / 100))
```


## What happens if you don’t use a closure? Make predictions, then verify with the code below.


```{r}
i <- 0
new_counter2 <- function() {
  i <<- i + 1
  i
}
```

## What happens if you use <- instead of <<-? Make predictions, then verify with the code below.


```{r}
new_counter3 <- function() {
  i <- 0
  function() {
    i <- i + 1
    i
  }
}
```